Contextual Combinatorial Cascading Bandits

### 2015-12-22 experiment.tex

@@

\section{Synthetic dataset}

Let $I=\{e_1,e_2,\dots,e_L\}$ be a set of arms, each associated with a $d$-dimensional vector $\mu_i$ randomly drawn from $\{x\in \mathbb{R}^d : \|x\|_2=1\}$. At round $t$, the context corresponding to the $i$-th arm, denoted as $x_{t,i}$, is generated using $x_{t,i}=(\mu_i+h\cdot b_{t,i})/\|\mu_i+h\cdot b_{t,i}\|_2$, where $b_{t,i}$ is randomly drawn from $\{x\in \mathbb{R}^d : \|x\|_2=1\}$ and $h$ is a constant throughout the experiment. The expectation of the Bernoulli realization of an arm $e\in I$ is $w_t(e)=\theta_\ast^Tx_i + \epsilon_{i,t}$, where $\theta_\ast$ s.t. $\|\theta_\ast\|_2=1$ is randomly initialized and holds throughout the experiment, and $\epsilon_{i,t}\sim N(\mu_i,\sigma_i)$ i.i.d. be the fluctuation. In this experiment, the set of avaiable superarms $S$ is $\{A\subseteq I:|A|=k\}$. The following approaches were tested:

\begin{enumerate}

  \item Li Shuai et al. Use linear regression on $\mathbf{O_t}$ observed arms and then UCB to select candidated.

  \item 2014 Qin Lijing et al. Same w/ Li but takes more information (from $\mathbf{O_t}$ to $k$) with a full feedback.

  \item 2015 Kveton Branislav et al. Combinatorial Cascading UCB which maintains its upper confidence bound purely by the historical payoff of the superarms selected. The contextual information $x_{i,t}$ is totally ignored so it can only catch the $\theta_\ast^T\mu$ part while suffers a lot from noisy.

  \item Random.

\end{enumerate}

\section{Movielens}

This section introduced Movielens dataset and its movie recommendation challenge. Let $L=\#\text{movies}$, Movielens is a matrix $A\in \{0,1\}^{\#\text{users}\cdot L}$ where each entry $A_{ij}$ is a boolean clickthrough indicator for the $i$-th user and the $j$-th movie. We split $A=A^1+A^2$, by randomly putting hot entries in $A$ into $A^1$ and $A^2$ according to a bernulli distribution. At round $t$, a user indexed $i_t$ is randomly selected from a predefined set of users, and the agent is required to recommend movies using $A^1$ and $\mathcal{H}_t$ such that $A^2_{i_tj}=1$ for as many those recommended $j$s as possible.

We formulate the movie recommendation problem into a combinatorial bandit problem. Let $A^1=USV^T$ be the SVD decomposition and the movies $I=\{e_1,\dots,e_L\}$ be the set of arms, we define the context associated with $e_j$, at round $t$, as $x_{t,e_j}=u_{i_t}^Tv_j$, where $u_l$, $v_l$ denote the $l$-th row of $U$, $V$, respectively. Upon received a super arm $A\in \{A\subseteq I: |A|=k\}$, the reward $r_t$ is calculated using its definition and $w_t(e_j)=A^2_{i_te_j}$. Some notes follows:

\begin{enumerate}

  \item Define $x_{t,e_j}=(u_{i_t}, v_j)$ is not applicable because the argmax over arms will ignore the stochastic part of the context.

  \item Split users into training and testing, as 2014 Qin Lijing et al. did, is not applicable because the context is constant for each arm.

  \item Measurement for Movielens is accuracy instead of regret because we have no access to the true $\theta_\ast$, if there is one.

\end{enumerate}

>>>>

\newcommand{\RR}{\mathbb{R}}
\newcommand{\cS}{\mathcal{S}}

@@

\section{Preliminary}

\subsection{Synthetic dataset}

Let $\cS = \{x \in \RR^d : \|x\|_2 = 1 \}$ be the unit ball of $\RR^d$. 
Let $E = \{1,...,L\}$ be the set of all base arms. 
We randomly choose $\theta_{\ast}$ with $\|\theta_{\ast}\|_2 = 1$ and randomly assign a $\mu_i \in \cS$ to $i$ for any $i \in E$.
At each time $t$, we choose $b_{t,i} \in \cS$ randomly for any base arm $i$.
Also we fix a constant $h$ to balance weights of $\mu_i$ and disturbance $b_{t,i}$.
Let $x_{t,i} = \frac{\mu_i + h b_{t,i}}{\|\mu_i+h\cdot b_{t,i}\|_2}$ be the context of base arm $i$ at time $t$.
And the weight for base arm $i$ at time $t$ is $w_t(i) = \theta_{\ast}^{\top}x_{t,i} + \epsilon_{t,i}$ where $\epsilon_{t,i} \sim N(\mu_i, \sigma_i)$ for fixed $\sigma_i$.

\subsection{MovieLens}

Let $L$ be the number of all movies and let $M$ be the number of all users. 
The MovieLens dataset is a big matrix $A \in \RR^{M \times L}$ where $A(i,j) \in \{0,1\}$ denotes whether user $i$ has watched movie $j$ or not.
We split $A$ to be $H + F$ by putting entry-$1$ of $A$ to $H$ and $F$ with probability $\sim \mathrm{Ber}(p)$ for some fixed $p$.
We can regard $H$ as know information about history 'What users have watched' and regard $F$ as future criterion.
We use $H$ to derive feature vectors of both users and movies by SVD decomposition $H = USV^{\top}$ where $U = (u_1; ...;u_M)$ and $V = (v_1;...;v_L)$.
At every time $t$, use $x_{t,i} = u_{i}v_j^{\top}$ as the context information of base arm $i$ and randomly choose a user $I_t$.
And use $w_t(j) = F(I_t,j)$ as the weight of base arm $j$.

Notice that for this case, fixed number of base arms, it might have problem if we use $(u_{I_t}, v_j)$ as context information.
Since to find the best arm, it is equivalent to find the best one with highest weights sum, so is equivalent to the best one with highest $\theta_{v}^{\top}x$.

The measurement for MovieLens is accuracy because we don't know the true $\theta_{\ast}$.

\section{Disjunctive case}

\subsection{Need to involve Contextual information}

We experiment both on synthetic data and MovieLens. We compare our method with $\gamma_k = 1$ to the algorithm in Cascading Bandits(ICML'2015) with $L= , K= ,$

\subsection{Need to involve position discount parameter $\gamma$}

We experiment both on synthetic data and MovieLens. We compare our method with $\gamma_k = \gamma^{k-1}$ to the algorithm in Cascading Bandits(ICML'2015) with $L= , K= , \gamma_k=1$.

\subsection{Cascading Information}

We experiment both on synthetic data and MovieLens. We compare our method with $\gamma_k = \gamma^{k-1}$ to the algorithm in Qin Lijing(2014) with $L= , K= , \gamma_k=1$.

\section{Conjunctive case}

\subsection{Need to involve Contextual information}

We experiment on synthetic data. We compare our method with $\gamma_k = 1$ to the algorithm in Cascading Bandits(ICML'2015) with $L= , K= ,$

\subsection{Need to involve position discount parameter $\gamma$}

We experiment on synthetic data. We compare our method with $\gamma_k = \gamma^{k-1}$ to the algorithm in Cascading Bandits(ICML'2015) with $L= , K= , \gamma_k=1$.

\subsection{Cascading Information}

We experiment on synthetic data. We compare our method with $\gamma_k = \gamma^{k-1}$ to the algorithm in Qin Lijing(2014) with $L= , K= , \gamma_k=1$.

\section{Results}
